What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-12 android-stacks.tex
changes on abstract.

This paper reports a study which mined the Java stack traces included in
159,048 issues reported on Android projects hosted in GitHub (482 projects) 
and Google Code (157 projsects). The goal of this study is to investigate whether the analysis of stack traces information 
could reveal bug hazards related to the exception handling code that may lead to a 
decrease in application robustness. A bug hazard is a circumstance that increases the 
chance of a bug to be present in the software. Overall 6,005 exception stack traces were extracted, and analyzed in 
combination with source code and bytecode analysis. 
Some of the outcomes of this study includes the identification of the following 
bug hazards: (i) unexpected exception wrappings (such as Errors being wrapped in checked exceptions) -
indicating that Java's hybrid exception model become fault-prone when it is not fully used in 
accordance with its purpose; (ii) undocumented runtime exceptions thrown by both the Android 
platform and third party libraries; and (iii) undocumented checked exceptions thrown by the Android Platform.
This study provides insights on such bug hazards and the robustness threats  
they impose not only to Android apps but also to other systems based on Java exception model.

\end{abstract}

>>>>

This paper reports a study which mined the Java stack traces included in
159,048 issues reported on Android projects hosted in GitHub (482 projects) 
and Google Code (157 projsects). The goal of this study is to investigate 
whether the analysis of stack trace information could reveal bug hazards related to the exception handling code,
 that may lead to a decrease in application robustness. 
 Overall 6,005 exception stack traces were extracted, and analyzed in 
combination with source code and bytecode analysis. 
Some of the outcomes of this study include the identification of the following 
bug hazards: (i) unexpected exception wrappings (such as Errors being wrapped in checked exceptions) -
indicating that Java's hybrid exception model become fault-prone when it is not fully used in 
accordance with its purpose; (ii) undocumented runtime exceptions thrown by both the Android 
platform and third party libraries; and (iii) undocumented checked exceptions thrown by the Android Platform.
This study provides insights on such bug hazards and the robustness threats  
they impose not only to Android apps but also to other systems based on Java exception model.

%A bug hazard is a circumstance that increases the chance of a bug to be present in the software.
\end{abstract}
